Statistical Analysis of Tournament Structures

### 2025-04-25 tournament analysis.qmd
paper.

	To evaluate a tournament’s effectiveness, we propose a numerical metric that quantifies how accurately it orders teams based on their true rankings. Tournament results can be viewed as a “message” attempting to convey the true team rankings. However, various factors introduce noise, leading to information loss. We use principles from information theory to measure this information loss across multiple tournament simulations to assess the reliability of different formats.

>>>>

```         
To evaluate a tournament’s effectiveness, we propose a numerical metric that quantifies how accurately it orders teams based on their true rankings. Tournament results can be viewed as a “message” attempting to convey the true team rankings. However, various factors introduce noise, leading to information loss. We use principles from information theory to measure this information loss across multiple tournament simulations to assess the reliability of different formats.
```
